\documentclass[times, twocolumn]{aastex63}
\bibliographystyle{aasjournal}
\usepackage{graphicx, graphics}
\bibliographystyle{aasjournal}
\usepackage{CJK}
\usepackage{amsmath, amssymb, bm}

\usepackage[nodayofweek]{datetime}
\newdateformat{monthyearday}{%
  \THEYEAR\ \monthname[\THEMONTH] \twodigit{\THEDAY}}
  
\DeclareMathOperator*{\argmin}{arg\,min}

%\received{}
%\revised{}
%\accepted{}
\published{\monthyearday\today}


\shorttitle{Pwned AASTeX}
\shortauthors{Ren et al.}

\usepackage{romannum}

\begin{document}
\pagenumbering{arabic}
\begin{CJK*}{UTF8}{gbsn}
\title{Pwned AASTeX}
\author[0000-0003-1698-9696]{Bin Ren (任彬)}\email{ren@jhu.edu}
\affiliation{Department of Physics and Astronomy, The Johns Hopkins University, 3701 San Martin Drive, Baltimore, MD 21218, USA}
\affiliation{Department of Applied Mathematics and Statistics, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218, USA}

\begin{abstract}
Modified from \url{https://journals.aas.org/aastexguide/}. The format of the titles have maximum similarity with the published version. The references are also well formatted. For example, \citet{ren17, ren18, ren18b, zhu16}. In the References section, the {\tt doi} is linked to the journal or proceeding name, and the {\tt adsurl} is linked to the volume and page number.


\end{abstract}

\keywords{blah blah}

\section{How to use}
Download {\tt aastex63.tex} (or {\tt aastex62.tex}), {\tt aasjournal.bst}, and {\tt orcid.png} from \url{https://github.com/seawander/aastex_pwned}.


\section{Section}
This is a section. The title is not capitalized and is in \textbf{bold face} now! Cite the appendix using {\tt \textbackslash ref}: \ref{append-a}.

\subsection{Blah blah}
This is a subsection. The title  is in \textit{italics} now!

\subsubsection{Blah blah}
This is a subsubsection.

\paragraph{This is a paragraph} 



\facilities{}

\software{}

\acknowledgments
This is the acknowledgements. I thank Xinyu Lu and Sihao Cheng for testing.


\appendix
\section{Example Appendix 1}\label{append-a}

This is an appendix. It's double columned and the title is in \textbf{bold face} now!

\subsection{Example Appendix 1 sub}\label{append-a-1}
This is the subsection of an appendix. It's double columned now!

\bibliography{refs}
\end{CJK*}
\end{document}